\section{PRACTICAL EXPERIENCE}

\cvexperince
{MLOps / Machine Learning Engineer}
{Present - Mar 2026}
{Liora / DataScientest}
{
  \item Weather Prediction: End-to-end pipeline, Training \& reproducibility, Deployment \& monitoring:
  \item Model development, inference, DVC repro, Dagshub, CI/CD, testing, MLflow \& Airflow integration.
  \item Model serving, orchestration, production workflows, monitoring with Prometheus \& Grafana.
  \item Data ingestion via APIs, preprocessing, feature creation and selection.
  \item% Leave an epty one every where!
}


\cvexperince
{Data Scientist}
{Sep 2025 - Dec 2025}
{Liora / DataScientest}
{
  \item Anomaly Detection in Automotive CAN Bus Data project:
  \item Big (\textbf{100M+} records), extreme class imbalance, time series, rational/non-rational data.
  \item Supervised/unsupervised ML models (XGBoost, SVM, Isolation Forest) → \textbf{99\%} Prediction accuracy.
  \item% Leave an epty one every where!
}


\cvexperince
  {Postdoctoral Researcher}
  {Feb 2022 -- Jan 2025}
  {University of Bremen,\\
  Hybrid Materials Interfaces Group}
  {
    \item Built scalable simulation workflows translating physical experiments into automated \textbf{Python/Bash pipelines}.
    \item Designed high-dimensional data processing logic for \textbf{50GB+} datasets with zero validation loss.
    \item Reduced \textbf{HPC} trial-and-error cycles by \textbf{50\%} through workflow automation.
    \item Optimized HPC workflows achieving a \textbf{10× speedup} (100+ hours → <12).
    \item%
  }

\cvexperince
  {Doctoral Researcher}
  {May 2018 -- Oct 2021}
  {Georg-August-Universität Göttingen,\\
  Institut für Materialphysik}
  {
    \item Modeled atomic-scale friction systems using \textbf{Python and C on HLRN HPC clusters}
    \item Improved computational efficiency by \textbf{10\%} via constraint monitoring and automated cleanup
    \item Reduced memory usage by \textbf{60\%} through optimized data structures and on-the-fly processing
    \item%
    }

\cvexperince
  {Accounting \& Operations Manager}
  {Jan 2007 -- May 2018}
  {Stone-Cutting Workshop, Iran}
  {
    \item Managed payroll, financial operations, and tax compliance for \textbf{25+ employees}
    \item Built cost-tracking and forecasting systems supporting production scaling
    \item%
  }
