
\letter{

Dear Hiring Team,\\

\vspace{0.0cm}

With a doctorate in theoretical physics and more than 14 years of experience in simulation, data analysis, and algorithm development, I am highly motivated to contribute to the ROSEN Group as a Physicist and Data Scientist in the field of ultrasound. My background combines rigorous applied mathematics, high-performance computing, and modern machine learning to transform complex measurement data into reliable, predictive insights for critical infrastructures.\\

Throughout my academic career, I have focused on the development and implementation of numerical and computational methods to analyze complex physical systems. During my PhD, I designed and implemented algorithmic frameworks to simulate and investigate frictional energy dissipation at the atomic scale. A key aspect of this work was the development of diagnostic analysis methods to identify the physical mechanisms behind observed effects. This required strong expertise in linear algebra, optimization techniques, and stochastic modeling, as well as efficient implementation in Python and C on HPC clusters.\\

As a postdoctoral researcher, I further strengthened my experience in descriptive, diagnostic, and forecasting methods. I developed automated simulation and data-processing pipelines for large-scale datasets (50GB+), translating experimental and simulation outputs into validated physical models. These workflows enabled hypothesis testing, identification of root causes, and prediction of system behavior under modified conditions. This predictive and diagnostic mindset directly aligns with the development of algorithms for object detection and classification from pipeline inspection data. In addition, I have basic knowledge of non-destructive testing methods, including ultrasound and EMAT, which motivates me to deepen my expertise in this field.\\

To complement my physics background, I have recently specialized as a Data Scientist and Machine Learning Engineer with a strong focus on MLOps. I am proficient in Python and experienced in supervised and unsupervised learning, having applied models such as XGBoost, SVM, and Isolation Forest to large-scale, highly imbalanced datasets (100M+ records), achieving 99\% accuracy in anomaly detection for automotive CAN bus data. In a hands-on weather prediction project, I designed and implemented a complete end-to-end pipeline including data ingestion, preprocessing, feature engineering, model training, experiment tracking (MLflow), data versioning (DVC), orchestration (Airflow), containerization (Docker), API deployment (FastAPI, NGINX), and monitoring (Prometheus, Grafana).\\

I am particularly motivated by ROSEN’s focus on predictive analytics, high-performance computing, artificial intelligence, and the provision of minimum viable products for customer-focused solutions. In this context, I can offer particular value in the following areas:

\begin{itemize}[leftmargin=*, label=\textbullet]
    \item \textbf{Algorithm Development \& Signal Processing:} Design of descriptive, diagnostic, and predictive algorithms rooted in applied mathematics, signal processing principles, and machine learning for robust object detection and classification.
    \item \textbf{High-Performance Computing \& Scalable Data Processing:} Extensive experience with HPC environments and large heterogeneous datasets, ensuring computational efficiency, scalability, and reproducibility.
    \item \textbf{MLOps \& Software Integration:} Development of reproducible pipelines and integration of intelligent services into production-ready environments, supporting interdisciplinary collaboration and customer-oriented MVP delivery.
\end{itemize}

I am a structured and independent team player who values interdisciplinary exchange and continuous learning. I would be delighted to discuss in a personal interview how my expertise in algorithm development, applied mathematics, and modern machine learning can contribute to the continued technological excellence of the ROSEN Group.

\vspace{0.8cm}

Kind regards,

\vspace{1em}
Saeed Amiri,\\
Dr.~rer.~nat.

}